### 2022-03-08 ms/PrestigeBias.tex
added summary

\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}

>>>>

\subsection{Using social influence to reverse harmful traditions \citep{harmful_traditions}}
Social influence could be a powerful tool to end traditions, harmful or advantageous. Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
\citet{harmful_traditions} suggest a mechanism called \textit{spillover}. By their definition, a spillover is when an intervention affect a large enough group in a target population, so that others not included in the intervention starts changing their behavior as well. In their research, they found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions. This is the same concept as our role-models, where a more prestigious individual will be copied more, therefore spreading his trait wider in the population. Their research support therefore in our assumption that there are social biases, conformist influence specifically. They also suggest a way to use this phenomena to change existing traditions in a population. It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind. 
\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}
